\documentclass{article}
\usepackage{graphicx}
\usepackage{pgfgantt}
\usepackage[section]{placeins}

\oddsidemargin = -0.25in
\headheight = 12pt
\textheight = 9in
\hoffset = 0pt
\topmargin = -0.5in
\headsep = 25pt
\textwidth = 7in
%\headwidth = 7in

\title{Improving Healthcare Access and Outcomes Using Decentralized Technologies and Applied Agorism}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Rapid Technological Evolution Empowering Individuals}

\subsection{Decentralized Technologies}



music, film industries\\
energy, etc.\\
p2p, bitorrent, file sharing, circumventing IP laws\\
blockchain, bitcoin, circumventing middleman institution\\
darknet markets\\
crowd funding, gofundme, medical bills, charity\\
sharing economy, uber, airb\&b, OpenBazaar products and services, platform cooperativism, eliminate middleman\\
decentralized web, ZeroNet, censorship resistance\\

%https://news.bitcoin.com/unsung-arcade-city-1000-meals/

\subsection{Applied Agorism}

Agorism is a philosophy detailing how to create a libertarian society of voluntary exchanges between people developed by Samuel Edward Konkin III and is expounded upon in his various works \cite{konkin2006new}\cite{konkin1995last}\cite{konkin2008agorist}. %Agorism advocates the use of counter-economics as a means for 

%Agorism is a revolutionary left-libertarian political philosophy that advocates the goal of bringing about a society in which all relations between people are voluntary exchanges by means of counter-economics.

%http://agorism.info/

%Agorism
%The ideology which asserts that the Libertarian philosophical position occurs in the real world in practice as Counter-Economics.
%Agorist
%Advocate or conscious practitioner of Counter-Economics, older terms include left libertarian and New Libertarian.
%Counter-Economics
%The study and/or practice of all peaceful human action which is forbidden by the State.
%Libertarian
%One who opposes state intervention, i.e., a defender of Liberty.
%Libertarian Left
%Activist, organization, publication or tendency which opposes parliamentarianism (electoral politics), defends Counter-Economists, and prefers alliances with radical and revolutionary tendencies to those with conservative ones.


\section{Healthcare Monopoly Complicit With Poor Access and Outcomes}

\subsection{Healthcare Market Distorted by Government Intervention}

licensing requirements\\
products sold constraints\\
hospital accreditation\\
drug patents

\subsection{Misdiagnosis}
% misdiagnosis rates
\cite{singh2014frequency}
% sharing problems

\subsection{Disenfranchised Patient Groups}

\subsubsection{Rare Diseases}

CVID

\subsubsection{Unusual Disease Presentations}

seronegative HIV

\subsubsection{Under Studied Diseases}

% rare diseases, rare presentations, emerging diseases
ME/CFS

\subsubsection{Emerging Diseases}

\subsection{Scarcity of Capable Doctors}

% developing world lack of doctors
% lack of capable doctors in developed & developing world

The developing world has a major shortage of doctors. For example Nigeria has roughly 14\% the number of doctors as OECD countries. \cite{wef2014}

% lack of access, scarcity
% unaffordable

vet anecdote

%Took my 13 year old dog to the vet and in one visit they aspirated a lump to check for fatty tissue or cancer, performed cheap ultrasound as vet was not board certified, vaccinations, physical.

%\subsection{Unjust Authoritarian System}
% systemic bias and inability to overule faulty doctor opinion
% systemic problem
% lack of patient power, authoritarian system, doctors in control
% patients prevented from ordering own tests

\cite{ferguson2007patients}

\subsection{Limited Direct Patient Testing, Doctor a Middleman}

Doctors are a middleman and serve as a barrier to access testing. Systemic problems exist where seeking alterate opinions does not guarantee improved outcome. Doctors are educated similarly and will have biases prevalent in the population. 

%pg.228 internet empowering individuals
\cite{CarsonDesktop}

\section{Patients Fighting Oppression by Practicing Agorism}

\subsection{Sharing Information}

% maybe talk about government efforts and the downsides to the approach
% who controls the data. dr. bias seeing information from other doctors, not unbiased

% concerns about anonymity
% de anonymizing cases and review

\subsubsection{Existing Platforms}
Forums: Phoenix Rising\\
PatientsLikeMe\\
Human Diagnosis Project\\
CrowdMed\\

\subsection{Accessing Information}
academic research papers\\
sci-hub.biz\\
% research data?
FindZebra\\
Enlitic
%https://www.reddit.com/r/MachineLearning/comments/4bhmqb/decentralized_deep_learning_on_a_blockchain_ai/

\cite{scholz2016platform}

% deep mind streams data sharing regulatory impedance
% importance of patient owned uncensorable platform that cannot be shutdown by government
% special treatment from government, DeepMind exclusive access to data that is tax payer funded

% patientslikeme have issues with this?

\subsection{Accessing Testing}

% access to lab tests (bloodborne)

online lab test services\\
walkin lab\\
personallabs\\
social engineering\\



Note that the UCSF Viral Diagnostics and Discovery Center is a research laboratory and cannot perform individual patient testing due to federal regulations. We are unable to perform clinical diagnostic testing, and only recommend that patients see their personal physician to discuss available clinical test options.

CLIA requires all entities that perform even one test, including waived test on ... "materials derived from the human body for the purpose of providing information for the diagnosis, prevention or treatment of any disease or impairment of, or the assessment of the health of, human beings" to meet certain Federal requirements. If an entity performs tests for these purposes, it is considered under CLIA to be a laboratory and must register with the CLIA program.

CLIA certification

%Depending on the circumstances, research testing can be either excepted from CLIA or subject to
%CLIA. Specifically, testing facilities may qualify to be excepted from CLIA certification if they
%meet the description of “research laboratories” provided by the CLIA regulations at 42 C.F.R.
%§ 493.3(b)(2). In accordance with that regulation, only those facilities performing research
%testing on human specimens that do not report patient-specific results may qualify to be
%excepted from CLIA certification. An example of a non-patient-specific result would be “10 out
%of 30 participants were positive for gene X.” The result in this example is a summary of the
%group data, and is not indicative of an individual’s health. An example of a patient-specific
%result would be “participant A was positive for gene X” in which the result is specific to
%participant A.

%http://vddc.ucsf.edu/collab.html

In US, going to states that allow direct patient testing
% data sharing medications
% access to medication

\subsection{Access to Procedures}

medical tourism\\


% access to procedures (pathology)
% access to procedures

\subsection{Access to Treatment}

HIV PreP in UK which is not available through the NHS but is cheaply available on the internet from suppliers in India and elsewhere.\\

%https://www.iwantprepnow.co.uk

\cite{wilson2017}\\

dallas buyers club, historical examples\\
foreign online pharmacies\\
forging precriptions\\
kevin carson anecdote\\
phoenix rising threads\\

Marijuana has been shown to compete with prescriptions drugs for conditions including chronic pain, depression, anxiety, nausea, and others \cite{bradford2016medical}. It's use for among cancer and HIV patients to alleviate symtoms is well known. Despite these benefits and the harm reduction when compared to opiates and other prescription drugs, in many states where it is still illegal, patients must break the law to acquire marijuana. Even in states with medical marijuana laws, government regulations can effectivley make it impossible to acquire legally. For example, in New York state, a very limited number of medical conditions are allowed. A prescription from a doctor must be acquired, yet only a few hundred doctors in the state have been licensed to give such prescriptions and there is no public directory of doctors to be able to know where to go to get a prescription. Not only that, but the patient must also purchase a license. 

Marijuana is a perfect example of decentralized medicene. It can be grown nearly anywhere with relative ease. Yet, as in New York, we see the government centralizing production by only allowing a limited number of producers who must acquire a license from the state which is extremely cost prohibitive. As is all too common, we see government intervention causing extremely limited access and high costs. If government really wanted to help patients, it could fully legalize marijuana and focus on ensuring home test kits and information is available to consumers to ensure that consumers have access to safe products. This is analagous to the abstience vs. safe sex issue. In this analogy, the government is preaching absitence by not allowing access to marijuana, yet patients who need it are going to use it anyways.

With regard to safety especially in people with compromised immune systems, there are some precautions that can be taken and room for improvement in making cost effective test kits available. For example, marijuana can be heated in an oven to kill some fungus and bacteria that may exist on the plant \cite{russo2014handbook}. Besides visual and olfactory inspection, there are also lab tests that can be performed to examine the plant for fungus, bacteria, mycotoxins, and other contaminants. In \cite{mckernan2015cannabis}, dispensary grade cannabis flowers were examined using PCR DNA analysis and other techniques to look for contaminants. 

growing own\\
darknet markets\\
alphabay\\


\section{Future of Agorism Applied to Healthcare}

\subsection{Sharing Economy Breakthroughs Applied to Healthcare}

%mainstream politics, Gary Johnson Uber-everything

\subsection{Machine Learning to Phase Out Doctors For Diagnosis}

\cite{topol2015patient}

\subsection{Homebrew Medical Devices Increasing Prevalence}

%the way in which falling capital outlays required for both information and material production was eroding the rationale for large organizations, and shifting the balance of power toward individuals, small groups and networks.  In particular, I focused on the radically reduced capital outlays required for manufacturing were giving rise to a low-overhead micromanufacturing economy in which the large quantities of land and capital to which the privileged classes had access were becoming increasingly irrelevant, and the material basis for the factory system and wage employment was collapsing.

\cite{carson2010homebrew}

%\subsection{Disease Discovery Big Data}


% virochip DNA printer
\cite{lausted2004posam}

% openPCR



% diabetes insulin pump open source project
https://openaps.org/outcomes/
OpenAPS
\cite{lewis2015introducing}




%https://www.reddit.com/r/Futurology/comments/2p6k20/im_jeremy_howard_enlitic_ceo_kaggle_past/

\cite{OpenSourceHealthcare}
\cite{carsonopensource}
\cite{MarketsNotCapitalism}
\cite{carsonhealthcare}

\bibliographystyle{ieeetr}
\bibliography{healthcare}


\end{document}